\chapter{Scope}

\section{In Scope}

\begin{enumerate}
    \item Project will improve upon the existing streaming graph sketching techniques. 
    \item Efficiency of running queries on various graph properties after the sketching process will be improved.
    \item New sketching techniques will be evaluated on a parallel framework.
\end{enumerate}

\section{Out of Scope}

\paragraph{}
There exists a number of methods for graph partitioning. The effect of these 
partitioning techniques will affect the results of the query efficiency and 
thus they will be considered during the experimentation phase and in presenting 
results. However no significant work or separate evaluation will be done with 
regard to graph partitioning. Improving partitioning techniques will be 
considered as out of scope for this research. 

\paragraph{}
Graph summarization could be mainly subdivided into Aggregation based, 
Attribute based, Compression and Application oriented. This research won’t 
explore the compression type graph summarization techniques. Much focus will 
be given to aggregation based sketching techniques. 

\paragraph{}
There are many security concerns with regard to the partitioning of streaming 
graphs and running sketching algorithms in a distributed environment. However 
the security aspects of sketch creation and partitioning will be considered 
as out of scope for this research as they are trivial to the holistic view 
of the research question, i.e, efficient sketching of streaming graphs. 