\section{Research standards \& tools for quality research}

\paragraph{}
This sections includes my awareness and usage of academic writing, 
reference managing software, referencing formats, plagiarism detectors as per 
the guidelines of the course \emph{SCS4124 - Final Year Project in Computer Science}.

\subsection{Academic writing}
\paragraph{}
I haven't done much academic writing before except for writing of a technical
article regarding \emph{Machine Learning over Encrypted Data}. However I have 
thoroughly read the best practices that should be followed when engaged in academic
writing. I was able to learn much about the academic writing styles by reading 
lot of research papers and white papers. 

\subsection{Reference managing software}

\subsubsection{Mendeley}
\paragraph{}
This was my initial choice for reference management. However the 1 GB 
cloud sync limit posed a big problem to me as I wanted to save lot of research 
materials. Mendeley was a good software, but I identified some bugs when I tried
to update the software. 

\subsubsection{Zotero}
\paragraph{}
I was introduced to Zotero by one of my colleagues. And it initially attracted
me because of the rich set of options that it had to manage a hard copy of the research 
articles. The software allows users to store either a soft link to the file or 
a hard copy. So this allowed me to keep a backup of my Zotero library and sync the 
folder to my own cloud storage which had much more capacity. Also there was a 
plugin called \emph{ZotFile} while allowed me to name the stored files according to
my desired collections. 

\subsection{Citations}
There is much debate in the internet about which citation style is more appropriate 
for each research article. Since this is was just a research proposal, I decided to 
go with the default citation style of Latex.

\subsection{Plagiarism detectors}
I've been using plagiarism detectors even before I started academic writing. 
There is no proper detector that I always use. I would just Google for free 
plagiarism detectors and go with the top result. But since these are mostly free 
versions, sometimes I have to split the text into 1000 word blocks and do 
plagiarism checks for each block.

% \subsection{Science Citation Index}
