\chapter{Research Tools}

\paragraph{}
This section introduces the tools used throughout the research so far. 

\section{Reference Managing Software}

\subsection{Mendeley}

\paragraph{}
Mendeley was our initial choice for reference management. However the 1 GB cloud sync limit posed a big problem as there were lot of reference material to be saved. Despite the reputation of Mendeley, we identified some bugs in the software when it started updating. 

\subsection{Zotero}

\paragraph{}
We switched to Zotero in order to eliminate the disadvantages of Mendeley. Zotero has a rich set of features to manage a local hard copy of the articles. The software allows users to store either a soft link to the file or a hard copy. So this allowed us to keep a backup of the Zotero library and sync the folder to our cloud storage which had much more capacity. Also there was a plugin called \emph{ZotFile} which facilitated us to name the stored files according to our desired collections. 

\section{Document Typesetting}

\subsection{LaTeX}

\paragraph{}
LaTeX was used in compiling this report. There was no decision to be made regarding this as LaTeX is the de facto standard of academic documents. 

\section{Publication Platforms}

\begin{itemize}
    \item ResearchGate
    \item arXiv
\end{itemize}

\section{Version Controlling}

\subsection{Git}

\paragraph{}
Version Controlling was used with both the algorithm implementation and the documents that were drafted in LaTeX. This made it easy to switch to previous points in time and work in branches. 